---
title: "Exploratory"
site: workflowr::wflow_site
output: workflowr::wflow_html
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = TRUE, 
  warning = TRUE, 
  error = FALSE
)
```

```{r libraries, message = FALSE, warning = FALSE}
library(skimr)
library(tidyquant)
library(tsibble)
```

```{r}
symbols <- c("IWM", "QQQ", "TLT", "SPY")
from    <- "2005-01-01"
to      <- "2015-01-01"
```

## Strategy

$$ \text{BTO} = \text{Adjusted} > \text{SMA (200) } \& \text{ RSI (2)} < 5 $$

$$ \text{STC} = \text{Adjusted} < \text{SMA (200) } \vee \text{ Close} > \text{SMA (5)} $$

### Data

```{r get-symbols}
df <- tq_get(c("IWM", "QQQ", "SPY"), from = "2005-01-01", to = "2015-01-01")
```

### Indicators

```{r indicators}
df <- 
  df %>% 
  group_by(symbol) %>% 
  arrange(date) %>% 
  tq_mutate(
    select     = adjusted, 
    mutate_fun = SMA, 
    n          = 5L, 
    col_rename = "SMA5"
  ) %>% 
  tq_mutate(
    select     = adjusted, 
    mutate_fun = SMA, 
    n          = 200L, 
    col_rename = "SMA200"
  ) %>% 
  tq_mutate(
    select     = adjusted, 
    mutate_fun = RSI, 
    n          = 2L, 
    maType     = SMA, 
    col_rename = "RSI2"
  ) %>% 
  mutate(
    chg1 = (adjusted - lag(adjusted, n = 1L))/adjusted, 
    chg3 = (adjusted - lag(adjusted, n = 3L))/adjusted, 
    chg5 = (adjusted - lag(adjusted, n = 5L))/adjusted, 
  )
```

### Signals

```{r signals}
df <- 
  df %>% 
  mutate(
    rsi2_lt_5    = if_else(RSI2 < 5,         TRUE, FALSE), 
    cl_gte_sma5  = if_else(adjusted >= SMA5,  TRUE, FALSE), 
    cl_lt_sma200 = if_else(adjusted < SMA200, TRUE, FALSE), 
    bto          = lag(rsi2_lt_5, n = 1L) & !lag(cl_lt_sma200, n = 1L),
    stc          = lag(cl_lt_sma200, n = 1L) | lag(cl_gte_sma5, n = 1L),
    position     = case_when(
      bto  ~ TRUE, 
      stc  ~ FALSE, 
      TRUE ~ NA
    ), 
    position     = na.locf(position, na.rm = FALSE)
  )
```

## Analysis

### Trade validation

```{r}
x <- which(df$bto)
#' Validate signals meat trade requirements
x %>% 
  map_lgl(
    .f = ~df$adjusted[(.x - 1)] > df$SMA200[(.x - 1)] & df$RSI2[(.x - 1)] < 5
  ) %>% 
  all()
```

### How many signals?

```{r}
skim(select(df, bto, stc))
```

Of all `bto` signals, 13% of the dataset for each symbol is TRUE; around 74% are TRUE for `stc` signals.

### Plot daily change where `bto` is TRUE

`chg1`

```{r}
skim(df %>% filter(bto) %>% select(starts_with("chg")))
```

Data doesn't suggest this is a favorable strategy; the mean for changes on bars 3 and 5 is -1% to -1.5% meaning on average this is a losing strategy. While max gains (`p100`) can be quite lucrative (up to 5%), max losses (`p0`) are much worse (5% to 11%). Standard deviation (`sd`) is rather broad as well, ranging between 1% and 2%.

`chg1`

```{r}
df %>% 
  filter(bto) %>% 
  ggplot() + 
  aes(x = chg1) + 
  geom_histogram(binwidth = 0.01)
```

skewed left; somewhat unimodal or symmetric

`chg3`

```{r}
df %>% 
  filter(bto) %>% 
  ggplot() + 
  aes(x = chg3) + 
  geom_histogram(binwidth = 0.01)
```

skewed left

`chg5`

```{r}
df %>% 
  filter(bto) %>% 
  ggplot() + 
  aes(x = chg5) + 
  geom_histogram(binwidth = 0.01)
```

skewed left

